\nt{\textbf{All} cells have the following;
    \begin{enumerate}
        \item Surrounding Membrane
        \item Chromosomes
        \item Cytosol
        \item Ribosomes.
    \end{enumerate}}
\dfn{Prokaryotic Cells}{They are defined as being, having, or including:
    \begin{enumerate}
        \item Non-membrane-bound organelles
        \item Nucleoid
    \end{enumerate}
    \nt{Prokaryotes include \textit{Bacteria} and \textit{Archaea}. They both differ genetically.}}
\dfn{Eukaryotic Cells}{They are defined as being, having, or including:
    \begin{enumerate}
        \item Membrane-bound organelles, including a nucleus.
        \item Multicellular potential.
    \end{enumerate}
    \nt{There is a limit on how big a cell can get. This is defined by the square-cube law. As surface area squares, the volume gets cubed.}}
\thm{Cellular Evolution}{Current Evidence indicates that eukaryotes evolved from prokaryotes between 1 and 1.5 billion years ago.
\nt{There are two current theories on howthis happened:
    \begin{enumerate}
        \item Folding Theory: In short, we believe that parts of the cell membrane folded in on itself, pinched off, and became specialized cells.
        \item Endosymbiotic Theory: The \textit{mitochondria} and \textit{chloroplasts} were once prokaryotic and somehow and for some reason became incorporated into another cell.
    \end{enumerate}}}

\section{Organelles}\label{sec:organelles}
\dfn{Organelle}{Insert Def here.}
\dfn{Nucleus}{Manager of cell functions. It also contains DNA and the nucleolus.}
\dfn{Nuclear Membrane}{A double membrane, each made up of two layers, making four total. It is selectively porous.}
\dfn{Nucleolus}{A darker spot in the nucleus where RNA and ribosomes are made.}
\dfn{Ribosome}{Produces proteins; made in the nucleolus}
\dfn{Endomembrane System}{Made up of all internal membranes in a cell; a continuous system. Vesicles bud off from and attach to membrane systems; transport shuttles.}
\dfn{Endoplasmic Reticulum}{Two Types;
    \begin{enumerate}
        \item [-] Smooth: No ribosomes.
        \item [-] Rough: Has ribosomes.
    \end{enumerate}}
\dfn{Vesicles}{Transporters.}
\dfn{Golgi Body/Apparatus}{Packages proteins; leaves on the trans side.}
\dfn{Lysosome}{Breaks down things; contains digestive enzymes.}
\dfn{Vacuole}{Store things, such as water.}
\dfn{Plastids}{Double Membrane.
\nt{\textit{Plastid}, a double membrane $\neq$ \textit{Plasmid}, prokaryotic DNA}}